Age-related changes in plant growth and traits

### 2016-11-30 scripts/RA_figs_201601129.Rmd
work on RA figures

###playing with variables to try and show meaningful RA plots despite negative leaf growth values
``` {r}
if (min(SummaryInd$growth_leaf) <= 0) {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf - SummaryInd$growth_leaf_min + 1
} else {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf
}

@@

SummaryInd$growth_leaf_no_neg_values = SummaryInd$growth_leaf
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$growth_leaf_no_neg_values[i] < 0) {
  SummaryInd$growth_leaf_no_neg_values[i] = SummaryInd$repro_inv[i]*.01
  }
}

SummaryInd$growth_leaf_fixed_max = SummaryInd$growth_leaf
SummaryInd$RA_fixed_max = SummaryInd$RA_leaf_area
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$RA_leaf_area[i] < 0) {
  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
  SummaryInd$RA_fixed_max[i] = 1.1 
  }
   if (SummaryInd$RA_leaf_area[i] > 1) {
  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
  SummaryInd$RA_fixed_max[i] = 1.1
  }
}

SummaryInd$leaf_replacement = SummaryInd$growth_leaf
SummaryInd$leaf_new = SummaryInd$growth_leaf
SummaryInd$leaf_new_nonzero = SummaryInd$growth_leaf
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$growth_leaf[i] < 0) {
  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_inv_gross[i]
  SummaryInd$leaf_new_nonzero[i] =.1
  SummaryInd$leaf_new[i] = 0
  }
   if (SummaryInd$growth_leaf[i] > 0) {
  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_shed[i]
  SummaryInd$leaf_new[i] = SummaryInd$growth_leaf[i]
  SummaryInd$leaf_new_nonzero[i] =SummaryInd$growth_leaf[i]
  }
}

SummaryInd$repro_inv_nonzero = SummaryInd$repro_inv
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$repro_inv[i] < .0001) {
    SummaryInd$repro_inv_nonzero[i] = .1
  }
}

plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.spp(species),pch=16)
abline(0,1)

plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.age(age),pch=16)
abline(0,1)

scatterplot3d(log(SummaryInd$repro_inv_nonzero),log(SummaryInd$leaf_new_nonzero),log(SummaryInd$leaf_replacement),color=col.spp(SummaryInd$species),pch=16,type="h",lty.hplot=3)

scatterplot3d(log(SummaryInd$leaf_replacement),log(SummaryInd$leaf_new),log(SummaryInd$repro_inv),color=col.spp(SummaryInd$species),pch=16,type="h", lty.hplot=3)

scatterplot3d(log10(SummaryInd$leaf_replacement),log10(SummaryInd$leaf_new),log10(SummaryInd$repro_inv_nonzero),color=col.spp(SummaryInd$species),pch=16,grid=TRUE,type="h", lty.hplot=3,lwd=.2,xlim=c(-1,6),ylim=c(-1,6),zlim=c(-1,6))

planes3d(0, x.coef = 1, y.coef = 1, lty = "dashed",)

par(mfrow=c(1,1), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
```
  data <- data %>% mutate(
    total_inv = repro_inv + growth_leaf + leaf_replacement + growth_stem,
    prop_repro = repro_inv / total_inv,
    prop_leaf_expand = (repro_inv + growth_leaf)/total_inv,
    prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
    prop_stem = total_inv/total_inv
  )

View(data)

```{r}
pdf("figs2/RA/Figure_1_stacked_lines.pdf", height=11.5, width=8)
plot
par(mfrow=c(4,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2))

  data[[spp]] <- data[[spp]] %>% mutate(
    total_inv = repro_inv + growth_leaf + leaf_replacement + growth_stem,
    prop_repro = repro_inv / total_inv,
    prop_leaf_expand = (repro_inv + growth_leaf)/total_inv,
    prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
    prop_stem = total_inv/total_inv
  )

  if(spp=="BAER"|spp=="EPMI"|spp=="GRBU"|spp=="HATE"|spp=="PELA"|spp=="PUTU"|spp=="LEES"|spp=="PEPU") {
  polygon(x=c(1.4,32,32,1.4),y=c(1,1,0,0),col="burlywood4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
                                           data[[spp]]$prop_leaf_replacement[5],data[[spp]]$prop_leaf_replacement[6],0,0),col="darkseagreen4",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
                                         data[[spp]]$prop_leaf_expand[5],data[[spp]]$prop_leaf_expand[6],0,0),col="darkseagreen2",density=NA)
  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
                                          data[[spp]]$prop_repro[5],data[[spp]]$prop_repro[6],0,0),col="coral3",density=NA)
  text(20,data[[spp]]$prop_repro[6]*.4,"reproductive")
  text(1.5,data[[spp]]$prop_leaf_expand[1]*.3,"additional leaves",adj=0)
  text(5,data[[spp]]$prop_leaf_replacement[4]*.6,"replacement leaves",adj=0)
  text(15,0.9,"additional stems",adj=0)
  }
  extra.top.left.logx(labels.spp.full(spp),3,1)
}

-#Figure 1 Different species have different RA values. But biggest shift in RA is with age
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
#pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
win.metafile("figs2/RA/Figure_1_leaf_vs_repro.wmf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("leaf investment, scaled to be positive (mg)",1,line=2,outer=TRUE)
dev.off()
```

#Figure 1 - shed leaves, gross leaf production
```{r}
pdf("figs2/RA/Figure_0_gross_leaf_inv.pdf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2)) 
plot(leaf_shed ~ leaf_inv_gross,SummaryInd,log="xy",pch=16, col=col.spp(species),xlim=c(1,10^7),ylim=c(1,10^7))
abline(0,1)
plot(leaf_shed ~ leaf_inv_gross,SummaryInd,log="xy",pch=16, col=col.age(age),xlim=c(1,10^7),ylim=c(1,10^7))

abline(0,1)

dev.off()

scatterplot3d(SummaryInd$leaf_shed,SummaryInd$leaf_inv_gross,SummaryInd$repro_inv,log="xyz",color=col.spp(SummaryInd$species),pch=16)

ternary <- dplyr::select(SummaryInd,species,age,leaf_shed,growth_leaf,pack_disp_costs,seed_costs,embryo_endo_size)
ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
ternary$post_poll <- 100-ternary$per_poll
ternary$per_seed <-100*ternary$embryo_endo_size/ternary$seed_costs
ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs

mod_poll <- sma(per_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_seed <- sma(per_seed~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_disp <- sma(per_disp~seed_costs,ternary,slope.test=0,method="OLS",log="x")
mod_post_poll <- sma(post_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")

costs_per_seed <- as.data.frame("costs for seed (%)")
costs_per_seed <- cbind(costs_per_seed,dplyr::select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")

costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)

costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)

write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)

win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
plot

plot(per_seed~seed_costs,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seed_costs")
points(per_poll~seed_costs,ternary,col="red",pch=16,cex=2)
points(per_disp~seed_costs,ternary,col="blue",pch=16,cex=2)

abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
legend("topright",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
v <- sqrt(ternary$seed_costs/500)
ternary$horz <- c(1.8,1.3,1.2,-0.3,0.6,0.6,0.5,-0.2,1.3,1.7,1.4,-0.2,-0.3,-0.3)
ternary$vert <- c(v[1]*-1.7,v[2]*1.1,v[3]*1.2,v[4],v[5]*-2.3,v[6]*4.5,v[7],v[8]*1.6,v[9],v[10]*0.2,v[11],v[12],v[13],v[14])
ternary = ternary[with(ternary, order(-seed_costs)), ]
label <- 20

dev.off()
library(ggtern)
win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(2,2,2,2), mai=c(2,2,2,2))

ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
      geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp(ternary$species)) +
      theme_bw() + 
      theme_showarrows() +
      geom_text(label=ternary$species, color="black", hjust=ternary$horz, 
                 vjust=ternary$vert,size=2) +
      ggtitle("Seed cost components")+
      labs(T="embryo+endosperm",L="pre-pollination",R="provisioning")+
      Tarrowlab("embryo + endosperm weight (%)")+
      Larrowlab("pre-pollination costs (%)")+
      Rarrowlab("provisioning costs (%)")+
      theme(plot.title = element_text(size=11,face="bold"))+
      theme(tern.axis.title.T = element_text(size=9,face="plain"))+
      theme(tern.axis.title.L = element_text(size=9,face="plain",hjust=0,vjust=1.7))+
      theme(tern.axis.title.R = element_text(size=9,face="plain",hjust=1,vjust=1.7))+
      theme(tern.axis.arrow.text = element_text(size=9,face="plain"))+
      theme(tern.axis.arrow.start= 0.2)+ 
      theme(tern.axis.arrow.finish=0.8)

```

#Figure 1 - alternate rendition, not scaling leaf investment to be positive, reassigning "negative" leaf investment individuals to RA =1.1
```{r}
pdf("figs2/RA/Figure_1_alt_leaf_vs_repro.pdf", height=4.3, width=8)
plot

par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2))

plot(repro_inv~(growth_leaf_fixed_max), subset(SummaryInd), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

plot(repro_inv~growth_leaf_fixed_max, subset(SummaryInd), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)

mtext("leaf investment (mg)",1,line=2,outer=TRUE)
dev.off()
```

#Figure 2 - RA schedules for species, including indication of schedule-type
```{r}
win.metafile("figs2/RA/Figure_2_RA_schedules.wmf", height=11, width=8)
plot
#pdf("figs2/RA/Figure_2_RA_schedules.pdf", height=11, width=8)
par(mfcol=c(5,3), cex=1, omi=c(.7,.7,.1,.1), mai=c(0.15,.15,0.05,0.05))

@@

  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
      } else{}
  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
    axis(2, at=c(-0,0.5,1,1.5), labels=c(-0,0.5,1,1.5),cex.axis=.8,las=1)
  } else{}
  extra.top.left.logx(labels.spp.full(spp),3)
  extra.bottom.left.logx(data3[[spp]]$RA_type,1,0.8)
}

@@

Table_01 <- as.data.frame(select(SummarySpp[["mean"]],species,RA_leaf_area,embryo_endo_size,LMA,wood_density,growth_shoot_length,seed_count))
Table_01 <- dplyr::right_join(Table_01,test2,by="species")
Table_01$RA_per_year <- Table_01$RA_leaf_area/Table_01$lifespan

win.metafile("figs2/RA/Figure_3_maxRA_correlates.wmf", height=11, width=8)
plot
par(mfcol=c(3,2), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2))

plot(maxRA_leaf_area~lifespan,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("lifespan (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
mod <- lm(log10(lifespan)~maxRA_leaf_area,Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
mtext("maximum RA",2,outer=TRUE,line=1)

plot(maxRA_leaf_area~mature,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("age at maturity (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
mod <- lm(mature~log10(maxRA_leaf_area),Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

plot(maxRA_leaf_area~embryo_endo_size,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n",xlim=c(.005,30),xaxt="n")
mtext("embryo + endosperm weight (mg)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
axis(1, at=c(.01,.1,1,10), labels=c(.01,.1,1,10),las=1)
mod <- lm(log10(embryo_endo_size)~maxRA_leaf_area,Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")

plot(maxRA_leaf_area~maxH,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("maximum height (mm)",1,outer=FALSE,line=2)
mod <- lm(log10(maxH)~maxRA_leaf_area,Table_01)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

@@

plot(maxRA_leaf_area~wood_density,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
mtext("wood density",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
mod <- lm(wood_density~maxRA_leaf_area,Table_01)
extra.top.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
dev.off()

write.csv(Table_01, file="figs2/RA/Table01_maxRA_correlates.csv",row.names=FALSE)

plot(RA_per_year ~ maxRA_leaf_area,Table_01,col=col.spp(species),pch=16,cex=2,log="y")
mod <- lm(maxRA_leaf_area~log10(RA_per_year),Table_01)
summary(mod)

plot(seed_count ~ maxRA_leaf_area,Table_01,col=col.spp(species),pch=16,cex=2,log="y")
```

#Figure 4a - reproductive vs leaf investment across plant weights
#Shows clearly how there is a crossover in leaf vs reproductive investment for all species, but magnitude of effect is very different
```{r}
win.metafile("figs2/RA/Figure_4a_investment.wmf", height=11, width=8)
plot
#pdf("figs2/RA/Figure_4a_investment.pdf", height=11, width=8)
par(mfcol=c(5,3), cex=1, omi=c(.3,.7,.1,.1), mai=c(0.5,.15,0.05,0.05))

@@

  points(repro_inv_log~total_weight_0,data[[spp]],pch=1,cex=1.2,col=col.age(data[[spp]]$age))
  points(leaf_repro_inv_log~total_weight_0,data[[spp]],pch=151,cex=1,col=col.age(data[[spp]]$age))
  extra.top.left.logx(labels.spp.full(spp),3)
  #arrows(data[[spp]]$total_weight_0,data[[spp]]$leaf_inv_log,data[[spp]]$total_weight_0,data[[spp]]$repro_inv_log,lwd=1,length=.08,
  #col=col.age(data[[spp]]$age))
  abline(0,0)
  axis(2, at=c(-4,-2,0,2,4), labels=c("","","","",""),cex.axis=.8,las=1,tck=-.03)

@@

#Figure 4b leaf area declines with age in some species, plateaus in others, and in a few continues to increase
```{r}
win.metafile("figs2/RA/Figure_4b_leaf_area_vs_age.wmf", height=11, width=8)
plot
par(mfcol=c(5,3), cex=1, omi=c(.5,.4,.1,.1), mai=c(0.15,.5,0.05,0.05))
xvar <- "age"
yvar <- "leaf_area"

>>>>

#new variables
``` {r}
SummaryInd$growth_leaf_fixed_max = SummaryInd$growth_leaf
SummaryInd$RA_fixed_max = SummaryInd$RA_leaf_area
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$RA_leaf_area[i] < 0) {
  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
  SummaryInd$RA_fixed_max[i] = 1.1 
  }
   if (SummaryInd$RA_leaf_area[i] > 1) {
  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
  SummaryInd$RA_fixed_max[i] = 1.1
  }
}

@@

```
#Figure 2 - RA schedules for species, including indication of schedule-type
```{r}
win.metafile("ms/RA/Figure_2_RA_schedules.wmf", height=11, width=8)
plot
#pdf("figs2/RA/Figure_2_RA_schedules.pdf", height=11, width=8)
par(mfcol=c(5,3), cex=1, omi=c(.7,.7,.1,.1), mai=c(0.15,.15,0.05,0.05))

@@

  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
      } else{}
  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
    axis(2, at=c(-0,0.5,1,1.5), labels=c(-0,0.5,1,1.5),cex.axis=.8,las=1)
  } else{}
  extra.top.left.logx(labels.spp.full(spp),3,1)
  extra.bottom.left.logx(data3[[spp]]$RA_type,1,0.8)
}

@@

Table_01 <- as.data.frame(select(SummarySpp[["mean"]],species,RA_leaf_area,embryo_endo_costs,LMA,wood_density,growth_shoot_length,seed_count,scaled_seed_count))
Table_01 <- dplyr::right_join(Table_01,test2,by="species")
Table_01$lifetime_RA <- Table_01$lifespan*Table_01$RA_leaf_area
plot(Table_01$lifetime_RA~embryo_endo_costs,Table_01,col=col.spp(species),pch=16,log="x")

win.metafile("ms/RA/Figure_3_maxRA_correlates.wmf", height=11, width=8)
plot
par(mfcol=c(3,2), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2))

plot(maxRA_leaf_area~lifespan,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("lifespan (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
mod <- lm(log10(lifespan)~maxRA_leaf_area,Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
mtext("maximum RA",2,outer=TRUE,line=1)

plot(maxRA_leaf_area~mature,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("age at maturity (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
mod <- lm(mature~log10(maxRA_leaf_area),Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)

plot(maxRA_leaf_area~embryo_endo_costs,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n",xlim=c(.005,30),xaxt="n")
mtext("embryo + endosperm weight (mg)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
axis(1, at=c(.01,.1,1,10), labels=c(.01,.1,1,10),las=1)
mod <- lm(log10(embryo_endo_costs)~maxRA_leaf_area,Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")

plot(maxRA_leaf_area~maxH,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("maximum height (mm)",1,outer=FALSE,line=2)
mod <- lm(log10(maxH)~maxRA_leaf_area,Table_01)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)

@@

plot(maxRA_leaf_area~wood_density,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
mtext("wood density",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
mod <- lm(wood_density~maxRA_leaf_area,Table_01)
extra.top.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
dev.off()

write.csv(Table_01, file="ms/RA/Table01_maxRA_correlates.csv",row.names=FALSE)
```

#Figure 4a - reproductive vs leaf investment across plant weights
#Shows clearly how there is a crossover in leaf vs reproductive investment for all species, but magnitude of effect is very different
```{r}
win.metafile("ms/RA/Figure_4a_investment.wmf", height=11, width=8)
plot
#pdf("figs2/RA/Figure_4a_investment.pdf", height=11, width=8)
par(mfcol=c(5,3), cex=1, omi=c(.3,.7,.1,.1), mai=c(0.5,.15,0.05,0.05))

@@

  points(repro_inv_log~total_weight_0,data[[spp]],pch=1,cex=1.2,col=col.age(data[[spp]]$age))
  points(leaf_repro_inv_log~total_weight_0,data[[spp]],pch=151,cex=1,col=col.age(data[[spp]]$age))
  extra.top.left.logx(labels.spp.full(spp),3,1)
  #arrows(data[[spp]]$total_weight_0,data[[spp]]$leaf_inv_log,data[[spp]]$total_weight_0,data[[spp]]$repro_inv_log,lwd=1,length=.08,
  #col=col.age(data[[spp]]$age))
  abline(0,0)
  axis(2, at=c(-4,-2,0,2,4), labels=c("","","","",""),cex.axis=.8,las=1,tck=-.03)

@@

data <- as.data.frame(select(SummarySppAge[["mean"]],species,age, repro_inv,growth_leaf,leaf_replacement,growth_stem,diameter))
for(v in c("repro_inv","growth_leaf","leaf_replacement","growth_stem")) {
    i <- is.na(data[[v]])
    data[[v]][i] <- 0
  }

data$lifetime_repro_inv <- data$repro_inv
data$lifetime_growth_leaf <- data$growth_leaf

for (i in 1:length(data$diameter)) {
  if (data$age[i] == 2.4) {
  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*2.6
  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*2.6
  }
}

for (i in 1:length(data$diameter)) {
  if (data$age[i] == 5) {
  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*2
  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*2
  }
}

for (i in 1:length(data$diameter)) {
  if (data$age[i] == 7) {
  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*2
  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*2
  }
}

for (i in 1:length(data$diameter)) {
  if (data$age[i] == 9) {
  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*5
  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*5
  }
}

for (i in 1:length(data$diameter)) {
  if (data$age[i] == 32) {
  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*18
  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*18
  }
}

lifetime <- data %>%
            group_by(species) %>% 
            summarise(repro = sum(lifetime_repro_inv))

lifetime2 <- data %>%
            group_by(species) %>% 
            summarise(leaf_growth = sum(lifetime_growth_leaf))

lifetime <- merge(lifetime,lifetime2,by="species")

lifetime$RA <- lifetime$repro / (lifetime$repro + lifetime$leaf_growth)            
plot(RA~leaf_growth,lifetime,pch=16,col=col.spp(species),log="x")

#stacked lines
```{r}
#pdf("figs2/RA/Figure_1_stacked_lines.pdf", height=11.5, width=8)
#plot
par(mfrow=c(7,4), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2))
